### 2014-02-22 paper/retrofit.tex
wip

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te | diverge
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

@@

@@

@@

%% \and
%% \inferrule[I-getLabel]
%% { }
%% {|
%% iconf iS (lconf id il tS getLabel, ldots)
%% .->
%% iconf iS (lconf id il tS il, ldots)
%% |}

@@

%% \and
%% \inferrule[I-setLabel]
%% { |il canFlowTo il'| }
%% {|
%% iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
%% .->
%% iconf iS (lconf id il' tS (iniE unit), ldots)
%% |}

@@

%% \and
%% \inferrule[I-send]
%% {
%% |il canFlowTo il'|\\
%% |iS(id') = Q|\\
%% |iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
%% }
%% {|
%% iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
%% .->
%% iconf iS' (lconf id il tS (iniE unit), ldots)
%% |}

@@

%% \and
%% \inferrule[I-recv]
%% {
%% | filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
%% | iS' = iS[id mapsto io1 , ... , iok]|\\
%% | ie1'' = {ie'/ix1,id'/ix2} ie1|
%% }
%% {|
%% iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
%% .->
%% iconf iS' (lconf id il tS (iniE ie1''), ldots)
%% |}

@@

%% \and
%% \inferrule[I-noRecv]
%% {
%% | filter il (iS(id)) = nil|\\
%% | iS' = iS[id mapsto nil]|
%% }
%% {|
%% iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
%% .->
%% iconf iS' (lconf id il tS (iniE ie2), ldots)
%% |}

>>>>

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

@@

iTE  ::=  THole | iTE, lconf id il tS ie

@@

\and
\inferrule[I-evalCtx2]
{|
iS ,(iniTE (lconf id il tS ie))
.-.>
iS', (iniTE' (lconf id il' tS ie'))
|}
{|
iS ,(iniTE (lconf id il tS (iniE ie)))
.-.>
iS', (iniTE' (lconf id il' tS (iniE ie')))
|}

@@

@@

@@

@@

@@
